---
title: "assign4"
output: html_notebook
editor_options: 
  chunk_output_type: console
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

```{r}
library(RVerbalExpressions)
library(lubridate)
library(stringr)
library(tidyverse)
```


# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year.

```{r}
first_day <- years(2019) + months(c(1:12)) + days(1)
```


Write a function that given your birthday (as a date), returns how old you are in years.

```{r}
age <- function(birthday)
{
  duration <- today() - ymd({{birthday}})
  as.duration(duration)
}

age(19970626)

```


Write a function that given your birthday, returns the day of the week you were born on. 

```{r}
birthday_ofwk <- function(birthday)
{
  wday({{birthday}}, label = T)
}

birthday_ofwk(ymd(19970626))
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r}
fruit <- c("banana", "pineapple", "cherry")

str_view(fruit , ".......", match = T)
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)

```{r}
#?str_detect()
letters_vec <- c("asdfad", "thyrpyn")
  
str_detect(letters_vec, "^[^aeiou]+$")
```


Empirically verify the rule “i before e except after c”.

```{r}
i_b4_e <- c("achieve", "piece", "glacier")
str_detect(i_b4_e, "(cie|[^c]ei)")
```

Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.

```{r}
telrx <- rx() %>%
  rx_start_of_line() %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of(c("-.")) %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of(c("-.")) %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>%
  rx_end_of_line() %>%
  print()

grepl(telrx, c("217.377.3867", "217-377-2867", "EM7.377.4322"))
```

# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*
# YES REPLACE MY GRADE FOR ASSIGNMENT 3

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

